---
title: "Quarto report on ebola cases in 3 different countries"
author: "Flurina Jenal"
date: "`r date()`"
format:
  html:
    toc: true
    code-fold: show
    df-print: paged
    embed-resources: true
  pdf:
    toc: true
editor: visual
---

This Quarto report was created in the course "Projects in R" from the Public Health Science curriculum. It shows the numbers and figures produced by the Ebola outbreak data (2014-2016) from [data.world](https://data.world/).



```{r}
#| echo: false
#| warning: false

library(tidyverse)
library(ggplot2)
library(unibeCols)
library(here)

```

## Loading Ebola data and tidy dataframe

```{r}
#| warning: false
#| echo: false


# Tidy dataframe ----
ebola <- read_csv(here("data", "raw", "ebola.csv"))

ebola_arr <- ebola %>% 
  arrange(Date) %>% 
  select(date = Date, country = Country, cum_conf_cases = Cum_conf_cases) %>% 
  filter(date <= ymd("2015-03-31")) %>% 
  filter(country == "Guinea" | country == "Liberia" | country == "Sierra Leone")

ebola_arr
```

## Generating point plot for Ebola data

@fig-ebola-point shows all confirmed Ebola cases from in 3 different countries.

```{r}
#| warning: false
#| label: fig-ebola-point
#| fig-cap: Confirmed Ebola cases in Liberia, Guinea and Sierra Leone

# Point plot ----
ggplot(data = ebola_arr, 
                              mapping = aes(x = date, y = cum_conf_cases)) + 
  geom_point(aes(color = country, fill = country), 
             alpha = 0.7, shape = 21, size = 1.5) +
  scale_fill_manual(name = "country",
                    breaks = c("Guinea", "Liberia", "Sierra Leone"),
                    values = c(unibeGreenS()[2], unibeIceS()[2], unibeMustardS()[2])) +
  scale_colour_manual(name = "country",
                      breaks = c("Guinea", "Liberia", "Sierra Leone"),
                      values = c(unibeGreenS()[2], unibeIceS()[2], unibeMustardS()[2])) +
  scale_x_date(breaks = ymd(c("2014-08-01", "2014-10-01", "2014-12-01", "2015-02-01", "2015-04-01")),
               labels = c("Aug", "Oct", "Dec", "Feb", "Apr"),
               limits = ymd(c("2014-08-01", "2015-04-01"))) +
  ggtitle(label="Confirmed ebola cases before 2025-03-31 in 3 Countries") +
  xlab(label = "Time") +
  ylab(label = "# of confirmed cases") +
  theme_minimal()
```

## Loading plot from other script

Here I want to load the @fig-ebola-line from another script.
```{r}
#| label: fig-ebola-line
#| echo: false

knitr::include_graphics(here("output", "figures", "plot_ebola_point_v1.pdf"))
```

```{r}
sessionInfo()
```
